Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-22 paper.tex
Minor word change to make line-break prettier

\noindent The work presented in this paper is a fundamental step towards a more general project's goal to develop a stand-alone system that can guide a VI user to their destination with minimal user input or intervention. A complete system diagram is given is Figure~\ref{fig:control-loop}. This closed-loop system is conceptually similar to other classical control problems, where the difference between desired and actual state of a process is used to generate a control signal that changes the process itself.

>>>>

\noindent The work presented in this paper is a fundamental step towards an over-arching project's goal to develop a stand-alone system that can guide a VI user to their destination with minimal user input or intervention. A complete system diagram is given in Figure~\ref{fig:control-loop}. This closed-loop system is conceptually similar to other classical control problems, where the difference between the desired and actual state of a process is used to generate a control signal that changes the process itself.
